Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2018-12-15 paper/ms.tex
Update paper

\subsection{Local Midplane} \label{sec:local_midplane}
We now turn to defining the local midplane that an observer might measure if
they were situated in each of these galaxies. We place our imaginary observer
at the solar radius of $8.2\,\kpc$ and azimuth $\phi$, and consider stars
within a cylinder perpendicular to the fiducial disk.

For a given azimuth $\phi$ at the solar radius of $8.2\,\kpc$, we take the
median height of all star particles within a cylinder of radius $0.5\,\kpc$
and total height $2\,\kpc$. This median height is taken to be what our
imaginary observer would measure as the local Galactic midplane, and is
reported for each galaxy in Figure~\ref{fig:midplane}. We find that only $10$
iterations of this procedure are necessary for convergence. We bootstrap
resample $1000$ times and report the $95^{\text{th}}$ minus $5^{\text{th}}$
percentile as the dashed-line error bars.

To allow for potential small inaccuracies in the fiducial coordinate systems,
we also subtract the best fit $\text{A} \sin{\phi + \text{B}} + C$ curve from
the midplane as a function of azimuth. For $\text{A}$, the values are $-165$,
$45$, $9\,\pc$ and for $\text{C}$ the values are $-69$, $19$, and $-18\,\pc$
for m12i, m12f, and m12m, respectively. For the assumed solar radius of
$8.2\,\kpc$, we can approximate the angle offset for the $z$-axis from the
values of $\text{A}$ --- we compute $1.15$, $0.31$, and $0.06\,\deg$ for m12i,
m12f, and m12m. These angle offsets are consistent with the values given in
\citet{2018arXiv180610564S} for the difference between the $z$-axis as defined
by the gas and stars.

@@

Our analysis makes the assumption that a global midplane is well defined.
However, our results are also consistent with the notion that the global
midplane is not a well-defined concept.

>>>>

\subsection{Local Midplane} \label{sec:local_midplane}
We now turn to defining the local midplane that an observer might measure if
they were situated in each of these galaxies. We place our imaginary observer
at the solar radius of $8.2\,\kpc$ and azimuth $\phi$\footnote{Our erroneous,
immortal observer is also warp-drive capable.}, and consider stars within a
cylinder of radius $0.5\,\kpc$ and height $1\,\kpc$ perpendicular to the
fiducial disk.

This median height is taken to be what our observer would measure as the local
Galactic midplane at each $\phi$, and is reported for each galaxy in
Figure~\ref{fig:midplane}. We find that only $10$ iterations of this procedure
are necessary for convergence. We bootstrap resample $1000$ times and report
the $95^{\text{th}}$ minus $5^{\text{th}}$ percentile as the dashed-line error
bars. This bootstrap resampling is performed by first selecting all stars
within a height of $2\,\kpc$, resampling that selection, and then repeating
the $10$ iterations.

To allow for potential small inaccuracies in the fiducial coordinate systems,
we also subtract the best fit $\text{A} \sin{\left(\phi + \text{B}\right)} +
\text{C}$ curve from the midplane as a function of azimuth. For $\text{A}$,
the values are $-165$, $45$, $9\,\pc$ and for $\text{C}$ the values are $-69$,
$19$, and $-18\,\pc$ for m12i, m12f, and m12m, respectively \Gus{Double check
numbers}. For the assumed solar radius of $8.2\,\kpc$, we can approximate the
angle offset for the $z$-axis from the values of $\text{A}$ --- we compute
\Gus{$1.15$, $0.31$, and $0.06\,\deg$} for m12i, m12f, and m12m. These angle
offsets are consistent with the values given in \citet{2018arXiv180610564S}
for the difference between the $z$-axis as defined by the gas and stars.

@@
